MSAD_PCA_Walkthrough

### 2017-01-26 Simulation_Vignette.Rmd
Begin testing for "Dynamic" option addition. CURRENT ISSUE: when some states have alarms and others do not, how do we bind these together? How do we bind an xts object of zero width to an xts object with width?

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 4320,
                         updateFreq = 1440,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 2)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).
